\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Alibi Galeyev} \\ \vspace{1pt}
    \small +77471545502 $|$
    \href{mailto:vasya.sidr777@gmail.com}{\underline{vasya.sidr777@gmail.com}} $|$ 
    \href{https://github.com/alad1nks}{\underline{github.com/alad1nks}} $|$
    \href{https://t.me/asteslenko}{\underline{t.me/asteslenko}}
\end{center}


\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Higher School of Economics}{Moscow}
      {Bachelor of Applied Mathematics and Informatics}{Aug. 2020 -- Present}
  \resumeSubHeadingListEnd


\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Developer of Audit Trails service}{Dec. 2023 -- Mar. 2024}
      {Yandex Cloud}{Moscow}
      \resumeItemListStart
        \resumeItem{Improved secret validation logic}
        \resumeItem{Created and implemented new async topic writer for trails and dlq messages}
        \resumeItem{Updated amazon kinesis from v1 to v2}
        \resumeItem{Fixed a bug in writing dlq messages}
      \resumeItemListEnd

    \resumeSubheading
      {Developer of dating app}{Aug. 2023 -- Dec. 2023}
      {Matchmaker}{Moscow}
      \resumeItemListStart
        \resumeItem{Improved client-server interaction logic}
        \resumeItem{Updated the logic of navigation to Debug Screen}
        \resumeItem{Added custom view components according to design}
        \resumeItem{Refactored the ui module, improving the dark theme logic}
      \resumeItemListEnd

    \resumeSubheading
      {Developer of psychological application}{June 2023 -- Aug. 2023}
      {Psychological Essence}{Moscow}
      \resumeItemListStart
        \resumeItem{Added user profile screen and user profile settings screen}
        \resumeItem{Fixed bugs with auth and quizzes}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/alad1nks/DubovozkiAndroid}{DubovozkiAndroid}} $|$ \emph{Kotlin, Jetpack Compose, MVI, Hilt, Retrofit, Room, Coroutines}}{Dec. 2023 -- May 2024}
          \resumeItemListStart
            \resumeItem{Developed an Android mobile application with bus schedule for HSE Students using Jetpack Compose}
            \resumeItem{Published app to \href{https://play.google.com/store/apps/details?id=com.app.dubkiapp}{\underline{Play Market}} gaining 500+ downloads and an average 5/5-star review}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{\href{https://github.com/alad1nks/DubovozkiBackend}{DubovozkiBackend}} $|$ \emph{Kotlin, Spring Boot, h2}}{Dec. 2023 -- May 2024}
          \resumeItemListStart
            \resumeItem{Developed a backend for DubovozkiAndroid application}
            \resumeItem{Created bus schedule, registration, random coffee and admin panel}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{\href{https://github.com/alad1nks/SHCPCSD}{SHCPCSD}} $|$ \emph{Kotlin, Golang, Jetpack Compose, MVVM, Hilt, Room, Coroutines}}{May 2023 -- June 2023}
          \resumeItemListStart
            \resumeItem{Developed an Android mobile application for greenhouse plants using Kotlin}
            \resumeItem{Developed the server part using Golang}
            \resumeItem{Built graphs of temperature, humidity and light quality of plants}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Kotlin, Java, Golang, Python, C/C++} \\
     \textbf{Frameworks}{: Jetpack Compose, Dagger2, Hilt, Coroutines, RxJava3, Retrofit2, Room, Spring Boot} \\
     \textbf{Developer Tools}{: Git, Bash, Docker, CI, Firebase, AWS, Intellij} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib} \\
     \textbf{Databases}{: PostgreSQL, Redis}
    }}
 \end{itemize}


\end{document}
